---
title: "write up liner model"
author: "Misty O'Brien"
date: "4/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 

You can import the data directly from a link to its website.  Copy that link to the clipboard by right clicking on Raw Data and then copy link.
```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
## Now add in scatterplot

```{r}
basicNN + geom_point()
```
  
  
# Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The model shows that r-squared is 0.4706 and shows that the residual standard error is 1.226

```{r}
newdata=data.frame(GRIP=94,ARM=88)
predict(model.1,newdata,interval="prediction")
```


# now add the model fit to our plot
  

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

The equation of SIMS is explained by ARM is
SIMS=-4.1+ 0.0545* ARM

## Model 2 SIM~GRIP
```{r}
basicBB <- ggplot(data,aes(y=SIMS,x=GRIP))
```
## Now add in scatterplot

```{r}
basicNN + geom_point()
```
  
  
# Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

# Inferential  (Build linear model)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
predict(model.2,newdata,interval="prediction")
```


# now add the model fit to our plot
  

```{r}
basicBB + geom_point() + geom_smooth(method=lm)
```

The equation of SIMS is explained by GRIP is
SIMS=-4.1+ 0.045* GRIP
The model shows that r-squared is 0.4094 and shows that the residual standard error is 1.295


## Model 3 SIM~ARM+GRIP

# Numerical results

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
  
# Inferential  (Build linear model)
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
predict(model.3,newdata,interval="prediction")
```

The equation of SIMS is explained by ARM is
SIMS=-5.43+0.037* ARM + 0.024* GRIP
The model shows that r-squared is 0.5422 and shows that the residual standard error is 1.144. The model is better then the last two due to the residual standard error is lower and the r-squared is higher than the others.
## ANOVA Test
```{r}
anova(model.1,model.3)
```
We found that the p=0.0000049 due to the p-value being so low we reject the null hypothesis and conclude that the best model for predicting SIMS is model 3. 
## Conclusion

From the data found we see the r-square of model 1 is 0.4706, model 2 is 0.4094 and model 3 is 0.5422, this shows thats model 3 is the better model. From the anvoa test p-value is 0.0000049 we reject the null hypothesis. 